Microbiome analysis - cohort figures

### 2020-09-30 code/R_markdown/P2_cohort.Rmd
revision updates

df_plot = merge(DOB_df, total_diarrhea %>% group_by(CHILDID) %>% summarize(n_diarr = n()), 
  by = "CHILDID", all = T)
df_plot$n_diarr[is.na(df_plot$n_diarr)] = 0
df_plot = merge(df_plot,as(sample_data(subset_samples(ps, pre_detection == F)),'data.frame'),
                by.x = "CHILDID", by.y = "Child.ID", all = T) %>% 
  select(CHILDID, DOB, n_diarr,symptomatic)

>>>>

df_plot = merge(DOB_df, total_diarrhea %>% group_by(CHILDID) %>% summarize(n_diarr = n()), 
  by = "CHILDID", all = T)
write.csv(df_plot$CHILDID,"/Users/maureencarey/local_documents/work/crypto_microbiome/manuscript_drafts/info_for_dbGaP/abx_samples.csv", row.names=FALSE)
df_plot$n_diarr[is.na(df_plot$n_diarr)] = 0
df_plot = merge(df_plot,as(sample_data(subset_samples(ps, pre_detection == F)),'data.frame'),
                by.x = "CHILDID", by.y = "Child.ID", all = T) %>% 
  select(CHILDID, DOB, n_diarr,symptomatic)
